The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-30 paper/ms.tex
url

\caption{\label{hrdiagram}
Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \texttt{gaia-kepler.fun} crossmatch and calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal.}
\end{figure*}

@@

This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement. This work made use of the gaia-kepler.fun crossmatch database created by Megan Bedell.

>>>>

\caption{\label{hrdiagram}
Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and calibrated distances from \citet{gaiadists}. The smear sample includes giants and hot main-sequence stars. Those giants for which TRES spectroscopy have been obtained are highlighted in teal.}
\end{figure*}

@@

This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement. This work made use of the \url{gaia-kepler.fun} crossmatch database created by Megan Bedell.
